


### IBD {background-color="#7A00E6"}

#### Expression distribution of `r target_gene` in cells of the human intestinal tract(PMID34497389) {.smaller}


```{r}
# maybe we can use column
```


::: {.panel-tabset}

##### Expression

```{r}
make_plot(gene = target_gene,
          gse = 'PMID34497389'
          )
```

- `r target_gene` expression is enhanced in 


##### CellCount

```{r}
gsetable(gse = 'PMID34497389')
```

##### StudyMeta

```{r}
make_st('PMID34497389')
```

:::


#### Expression distribution of `r target_gene` in IBD patient samples {.smaller}

##### GSE164985/colonic mucosa

::: {.panel-tabset}

##### Expression

```{r}
#| label: GSE164985


make_plot(gene = target_gene,
          gse = 'GSE164985'
          )
```


- `r target_gene` expression is enhanced in 


##### CellCount

```{r}
gsetable(gse = 'GSE164985')
```

##### StudyMeta

```{r}
make_st('GSE164985')
```


:::


#### Expression distribution of `r target_gene` in CD patients(GSE202052/ileal mucosal) {.smaller}


::: {.panel-tabset}

##### Expression

```{r}
#| label: GSE202052
#| 
make_plot(gene = target_gene,
          gse = 'GSE202052'
          )
```


- `r target_gene` expression is enhanced in 


##### CellCount

```{r}
gsetable(gse = 'GSE202052')
```


##### StudyMeta

```{r}
make_st('GSE202052')
```


:::


#### Expression distribution of `r target_gene` in UC patients(GSE125527) {.smaller}


::: {.panel-tabset}

##### Expression

```{r}
#| label: GSE125527
#| 
make_plot(gene = target_gene,
          gse = 'GSE125527'
          )
```


- `r target_gene` expression is enhanced in 


##### CellCount

```{r}
gsetable(gse = 'GSE125527')
```


##### StudyMeta

```{r}
make_st('GSE125527')
```


:::

