
### COPD {background-color="#7A00E6"}

#### Expression distribution of `r target_gene` in COPD patients(GSE168191/lung) {.smaller}

::: {.panel-tabset}

##### Expression

```{r}
#| label: GSE168191
make_plot(gene = target_gene,
          gse = 'GSE168191'
          )
```


- `r target_gene` expression is enhanced in 


##### CellCount

```{r}
gsetable(gse = 'GSE168191')
```

##### StudyMeta

```{r}
make_st('GSE168191')
```


:::



#### Expression distribution of `r target_gene` in COPD patients(GSE136831/lung) {.smaller}


::: {.panel-tabset}

##### Expression

```{r}
#| label: GSE136831
make_plot(gene = target_gene,
          gse = 'GSE136831'
          )
```


- `r target_gene` expression is enhanced in 


##### CellCount

```{r}
gsetable(gse = 'GSE136831')
```

##### StudyMeta

```{r}
make_st('GSE136831')
```


:::


#### Expression distribution of `r target_gene` in COPD patients(GSE173896/lung) {.smaller}

::: {.panel-tabset}

##### Expression

```{r}
#| label: GSE173896
#| 
make_plot(gene = target_gene,
          gse = 'GSE173896'
          )
```


- `r target_gene` expression is enhanced in 


##### CellCount

```{r}
gsetable(gse = 'GSE173896')
```


##### StudyMeta

```{r}
make_st('GSE173896')
```


:::

