

### Others {background-color="#7A00E6"}

#### Expression distribution of CAMK4 in IPF patients(GSE128033/lung) {.smaller}


::: {.panel-tabset}

### Expression

```{r}
#| label: GSE128033
#| 
make_plot(gene = target_gene,
          gse = 'GSE128033'
          )
```


- `r target_gene` expression is enhanced in 


### CellCount

```{r}
gsetable(gse = 'GSE128033')
```


:::


#### Expression distribution of CAMK4 in Asthma patients(GSE164015/bronchial tube) {.smaller}

::: {.panel-tabset}

### Expression

```{r}
# make_plot(gene = target_gene,
#           gse = 'GSE164015'
#           )
```


- `r target_gene` expression is enhanced in 


### CellCount

```{r}
# gsetable(gse = 'GSE164015')
```


:::


#### Expression distribution of CAMK4 in GVHD/sclerosis patients(GSE195452/skin) {.smaller}


::: {.panel-tabset}

### Expression

```{r}
#| label: GSE195452
#| 
make_plot(gene = target_gene,
          gse = 'GSE195452'
          )
```


- `r target_gene` expression is enhanced in 


### CellCount

```{r}
gsetable(gse = 'GSE195452')
```


:::

#### Expression distribution of CAMK4 in RA(GSE200815) {.smaller}


::: {.panel-tabset}

### Expression

```{r}
#| label: GSE200815
#| 
make_plot(gene = target_gene,
          gse = 'GSE200815'
          )
```


- `r target_gene` expression is enhanced in 


### CellCount

```{r}
gsetable(gse = 'GSE200815')
```


:::




