---
title: "Gene Expression"
subtitle: "Explore Gene Expression in scRNA datasets"
author: DDS
format: 
  pptx: 
    incremental: FALSE
    reference-doc: template.pptx
---


#### gene Expression distribution in PBMC(PMID35383111) {.smaller}

```{r}
#| include: false

library(tidyverse)
```


```{r}
# input your gene here
target_gene <- 'CAMK4'


# plot GSE expression bar plot
make_plot <- function(gene, gse) {
  scgene <- gene
  scGSE <- gse

  p_data <- vroom::vroom(glue::glue("./data/talk2data/{scGSE}_sc_meanCI.csv"),
    delim = ",",
    show_col_types = NULL
  )
  condition1 <- names(p_data)[[2]]
  celltype <- names(p_data)[[1]]
  genemean <- paste0(scgene, "_mean")
  genelow <- paste0(scgene, "_low")
  geneup <- paste0(scgene, "_up")

  p_data <- p_data %>%
    dplyr::select(1:2, starts_with({{ scgene }})) %>%
    dplyr::rename(
      "Condition" = all_of(condition1),
      "CellType" = all_of(celltype)
    )

  ggplot(p_data, aes(
    x = CellType,
    y = .data[[genemean]],
    fill = Condition
  )) +
    geom_col(position = "dodge") +
    geom_errorbar(
      aes(
        x = CellType,
        ymin = .data[[genelow]],
        ymax = .data[[geneup]]
      ),
      width = 0.4, colour = "orange",
      alpha = 0.9, linewidth = 1,
      position = position_dodge(.9)
    ) +
    paletteer::scale_fill_paletteer_d("ggsci::category20_d3") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90))
}


```


```{r}
make_plot(gene = target_gene,
          gse = 'PMID35383111'
          )
```


- `r target_gene` expression is enhanced in naïve/memory/effector T cells.

::: footer
Learn more: [talk2data](https://talk2data.pharma.aventis.com/t2d_balancer/)
:::


#### Expression distribution of CAMK4 in cells of the human intestinal tract (PMID34497389)


```{r}
# maybe we can use column
```


:::: {.columns}

::: {.column width="40%"}

```{r}
make_plot(gene = target_gene,
          gse = 'GSE202052'
          )
```

:::

::: {.column width="60%"}

```{r}
make_plot(gene = target_gene,
          gse = 'GSE202052'
          )
```

:::

::::


- `r target_gene` expression is enhanced in


#### Expression distribution of CAMK4 in IBD patient samples

##### GSE164985/colonic mucosa


```{r}
make_plot(gene = target_gene,
          gse = 'GSE164985'
          )
```

- `r target_gene` expression is enhanced in


---

THANK YOU!!







